Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/40-ocr-bench.tex
Fix refs in intro/contrib
Update OCR text/eval top keep one CER metric

% !TeX root = ../main-paper.tex
\section{OCR benchmark}

@@

\subsection{Metrics}
\textbf{OCR Q.A.} is performed after some text normalization of the OCR system outputs. Text normalization consists in
projecting Unicode characters onto the latin-1 \emph{charset} (whenever it makes sense) and removing extra symbols (hands,
crosses). Then, the predicted text is aligned with the reference text using standard tools from Stephen V. Rice's
thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip} and the Character Error Rates (CER) are computed at the entry level
and at the global level.

\begin{align}
\mathrm{CER} &=  \frac{\#Errors}{\text{Reference Text Length}} & & \mathrm{CER}_\mathrm{norm} =  \frac{\#Errors}{\text{Alignment Length}} 
\end{align}

@@

\subcaptionbox{}[.5\linewidth]{
\begin{tabular}{rll}
\toprule
            & CER & CER$_{norm.}$ \\
\midrule
Pero-OCR  & 3.78\% & 3.76\% \\   
Tesseract & 6.56\% & 6.45\% \\
Kraken    & 15.72\% & 15.46\% \\  
\bottomrule
\end{tabular}

\bigskip

\includegraphics[width=\linewidth]{images/ocr-eval-2.pdf}
}
\subcaptionbox{}[.5\linewidth]{
\includegraphics[width=\linewidth]{images/ocr-eval-1.pdf}
}
\caption{Character error rates at entry-level for Pero-OCR, Kraken and Tesseract. (a) Global CER and distribution of the CER per entry. (b)
joint plot of the per-entry error rate showing that Pero-OCR and Tesseract do not fail on the same entries.}  
\label{fig.ocr-results}
\end{figure}

>>>>

% !TeX root = ../main-paper.tex
\section{OCR benchmark}
\label{sec:ocr-xp}

@@

\subsection{Metrics}
\textbf{OCR Q.A.} is performed after some text normalization of the OCR system outputs. Text normalization consists in
projecting Unicode characters onto the latin-1 \emph{charset} (whenever it makes sense) and removing extra symbols
(hands, crosses). Then, the predicted text is aligned with the reference text using standard tools from Stephen V.
Rice's thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip}. The Character Error Rate (CER) is computed at the entry
level and at the global level defined as the ratio between the number of errors (insertions/deletions/substitutions)
over the reference text length.

@@

\subcaptionbox{}[.5\linewidth]{
\begin{tabular}{rlll}
\toprule
 & Pero-OCR  & Tesseract & Kraken \\    
\midrule
CER & 3.78\% & 6.56\% & 15.72\% \\  
\bottomrule
\end{tabular}
\bigskip

\includegraphics[width=\linewidth]{images/ocr-eval-2.pdf}
\medskip
}
\subcaptionbox{}[.5\linewidth]{
\includegraphics[width=\linewidth]{images/ocr-eval-1.pdf}
}
\caption{Character error rates at entry-level for Pero-OCR, Kraken and Tesseract. (a) Global CER and distribution of the CER per entry. (b)
joint plot of the per-entry error rate showing that Pero-OCR and Tesseract do not fail on the same entries.}  
\label{fig.ocr-results}
\end{figure}
